---
title: "2018 Licensed Angler Survey Trends"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  # word_document: default
  officedown::rdocx_document
always_allow_html: yes
---

```{r setup, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE, fig.width=7.5, fig.height=6.5}
knitr::opts_chunk$set(echo=FALSE, include=TRUE, warning=FALSE, error=FALSE, message=FALSE,  ft.align="left", fig.width = 7.4)
options(stringsAsFactors = FALSE)
#devtools::install_github("davidgohel/officer")
#devtools::install_github("davidgohel/officedown")
library(officedown)
library(rmarkdown)
library(likert)
library(knitr)
library(flextable)
library(stringr)
library(foreach)
library(tictoc)
library(tidyverse)

tic("run report")

source("..\\BaseFunctions.R") #load file of common functions
source("TrendTableFunctions.R") #load file of cross tab report functions
```

```{r getData, echo=FALSE}
#load data
#d<- base.loaddata.venues.2018()
#mydata<-base.loaddata.venues.2018()
#mydata<-base.loaddata.venues.all()
#mydata<-mydata[mydata$venue==3,]
#d<-base.loaddata(myYears=c("2002", "2012", "2018"), myVenues=c("mail", "email"))
#save(d, file="d_20190715_allyears_email_mail.rData")
load(file="d_20190715_allyears_email_mail.rData")

#load questions
#q<-base.loaddata.factorlevels()
#save(q, file="q_20180215")
load(file="q_20180215")

#load labels
l=read.csv(file="..\\..\\Data\\Labels.csv")

#load scales
s=read.csv(file="..\\..\\Data\\Scales.csv")

#load age distribution of permits for raking
load(file="../../data/AgeDistributions_2018.rData")
rm(myPermits2)

rakeVars<-data.frame(surveyYear=c(2018),
                    rakeVar=c("age_group"))
rakePopDists<-list(c(ageDist))

```

```{r createFunctions}
# CreateFlex<-function(x, mergeOnFirst=FALSE) {
#   require(officer)
#   require(flextable)
#   
#   bigborder=officer:: fp_border(color="black", width = 1.5)
#   smallborder=officer:: fp_border(color="black", width=0.75)
#   
#   myFlex<-  flextable(x) %>%
#     theme_zebra()
#   
#   if(mergeOnFirst==TRUE) {
#     #merge first column cells  
#     myFlex <-myFlex %>%
#         merge_v(j=1, part="body") 
#       #add border below merged cells in first column
#       myFlex<-myFlex %>%
#         border(border.bottom = smallborder, i=rle(cumsum(myFlex$body$spans$columns[,1] ))$values, part="body") 
#   }
#   
#   myFlex <- myFlex %>%
#     #border_outer(officer:: fp_border(color="black", width = 1.5), part="all") %>%
#     #add border above and below footer
#     border(border.bottom = bigborder, border.top = bigborder, part = "header") %>%
#     #add border at bottom of body
#     border(border.bottom = bigborder, i=nrow(myFlex$body$spans$rows), part = "body") %>%
#     padding(j=1, padding.left=3) %>%
#     align(align="left", part="all") %>%
#     fontsize(part = "header", size = 10) %>%
#     fontsize(part="body", size=8) %>%
#     bold(part="header") %>%
#     autofit() %>%
#     width(j = 1, width = 1.2)
#       
#   myFlex
#   }
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, A2, 2018)),"  ", caption.percents, sep="")`

```{r A2_NoFish}
CreateFt(
  ArrangeTable(
    base.summary.percent.selectOne(d, A2) %>% filter(Response=="No"),
    roundDigits=1
  )
)
```

```{r A2}
CreatePercPlot(base.summary.percent.selectOne(d, A2), freeScale = FALSE)

```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, A3, 2018)),"  ", caption.percents, sep="")`

```{r A3_whyNoFish}
CreateFt(
  ArrangeTable(
    base.summary.percent.selectOne(d, A3),
    roundDigits=1
  )
)
```

```{r A3}
CreatePercPlot(base.summary.percent.selectOne(d, A3))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, A4, 2018)),"  ", caption.percents, sep="")`

```{r A4_WaterbodyTypes}
myFields<-d %>% dplyr::select(contains("A4")) %>% select(-contains("Answered")) %>% names()
CreateFt(ArrangeTable(
  base.summary.percent.selectAll(d, myFields, myAnsweredVar = A4_Answered),
  roundDigits = 1))
```

```{r A4}
CreatePercPlot(base.summary.percent.selectAll(d , myFields, myAnsweredVar = A4_Answered))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, A5, 2018)),"  ", caption.percents, sep="")`

```{r A5_Methods}
myFields<-d %>% dplyr::select(contains("A5")) %>% select(-contains("Answered")) %>% names()
CreateFt(ArrangeTable(
  base.summary.percent.selectAll(d, myFields, myAnsweredVar = A5_Answered),
  roundDigits = 1))
```

```{r A5}
CreatePercPlot(base.summary.percent.selectAll(d, myFields, myAnsweredVar = A5_Answered))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, A6, 2018)),"  ", caption.percents, sep="")`

```{r A6_techniques}
myFields<-d %>% dplyr::select(contains("A6")) %>% select(-contains("Answered")) %>% names()
CreateFt(ArrangeTable(
  base.summary.percent.selectAll(d, myFields, myAnsweredVar = A6_Answered),
  roundDigits = 1))
```

```{r A6}
CreatePercPlot(base.summary.percent.selectAll(d, myFields, myAnsweredVar = A6_Answered))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, A7, 2018)),"  ", caption.medians, "  ", labels.distance, sep="")`

```{r A7_favoriteMiles}
CreateFt(ArrangeTableMedians(
  base.summary.medians(d, A7_miles)%>% mutate(CI=paste(CIupper, "/", CIlower, sep="")),
  roundDigits = 1) %>% select(-Response))
```

`r paste(trimws(GetQuestion(q, A8, 2018)),"  ", caption.percents, "  ", labels.distance, sep="")`

```{r A8_mostVisitiedMiles}
CreateFt(ArrangeTableMedians(
  base.summary.medians(d, A8_miles)%>% mutate(CI=paste(CIupper, "/", CIlower, sep="")),
  roundDigits = 1) %>% select(-Response))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, A9, 2018)),"  ", caption.percents, "  ", labels.satisfaction, sep="")`

```{r A9_satisfactionPerc}
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(d, A9),
  roundDigits = 1))
```

```{r A9}
CreatePercPlot(base.summary.percent.selectOne(d, A9), freeScale = FALSE)
```

```{r A9_satisfactionMean}
CreateFt(ArrangeTable(
  base.summary.means(d, A9),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, A10, 2018)),"  ", caption.means, sep="")`

```{r A10_parkPermits}
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(d, A10),
  roundDigits = 1))
```

```{r A10}
CreatePercPlot(base.summary.percent.selectOne(d, A10), freeScale = FALSE)
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, E7, 2018)),"  ", caption.percents, sep="")`

```{r E7_CO}
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(d, E7),
  roundDigits = 1))
```

```{r E7}
CreatePercPlot(base.summary.percent.selectOne(d, E7), freeScale = FALSE)
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, B1, 2018)),"  ", caption.percents, sep="")`

```{r }
CreateFt(
  ArrangeTable(
    base.summary.percent.selectOne(d,B1),
    roundDigits = 1)
)
```

<!---CHUNK_PAGEBREAK--->

```{r fig.height=7}
CreatePercPlot(base.summary.percent.selectOne(d,B1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, B1, 2018)),"  ", caption.ranks, sep="")`

```{r B1_rank}
op<-base.summary.percent.selectOne(d,B1) %>%
  group_by(Year) %>%
  arrange(-Value) %>%
  mutate(Rank=seq(1,length(Value))) %>%
  ungroup() %>%
  select(Year, Response, Value, Rank)

CreateFtRanks(ArrangeTableRanks(op))

```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, B2, 2018)),"  ", caption.percents, sep="")`

```{r }
myFields<-d %>% dplyr::select(contains("B2")) %>% select(-contains("_")) %>% select(-contains("Answered")) %>% names()
op<-base.summary.percent.selectAll(d, myFields, B2_Answered)
CreateFt(ArrangeTable(op,
    roundDigits = 1)
         )
```

<!---CHUNK_PAGEBREAK--->

```{r fig.height=7}
CreatePercPlot(base.summary.percent.selectOne(d,B1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, B2, 2018)),"  ", caption.ranks, sep="")`

```{r B2_rank}
myFields<-d %>% dplyr::select(contains("B2")) %>% select(-contains("_")) %>% select(-contains("Answered")) %>% names()

op<-base.summary.percent.selectAll(d, myFields, B2_Answered) %>%
  group_by(Year) %>%
  arrange(-Value) %>%
  mutate(Rank=seq(1,length(Value))) %>%
  ungroup() %>%
  select(Year, Response, Value, Rank)

CreateFtRanks(ArrangeTableRanks(op))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, B3, 2018)),"  ", caption.percents, sep="")`

```{r }
myFields<-d %>% dplyr::select(contains("B3")) %>% select(-contains("Answered")) %>% select(-contains("oth")) %>% select(-contains("any")) %>% names()
op<-foreach(i=myFields, .combine="bind_rows") %do% {
  data.frame(Species=i,
             ArrangeTable(
                base.summary.percent.selectOne(d %>% filter(!is.na(get(i))) %>% filter(as.numeric(get(gsub("3", "2", i)))==2),
                                            !!rlang::sym(i))),
             check.names = FALSE)
}

CreateFt(LabelResponses(op,l, responseField="Species"), headerColumn=Species, mergeOnFirst = TRUE)

```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, B3, 2018)),"  ", caption.means, "  ", labels.release, sep="")`

```{r }
myFields<-d %>% dplyr::select(contains("B3")) %>% select(-contains("Answered")) %>% select(-contains("oth")) %>% select(-contains("any")) %>% names()
op<-foreach(i=myFields, .combine="rbind") %do% {
  base.summary.means(d %>% filter(!is.na(get(i))) %>% filter(as.numeric(get(gsub("3", "2", i)))==2), !!rlang::sym(i))
}

CreateFt(ArrangeTable(LabelResponses(op, l)))
```


<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2018)),"  ", caption.percents, sep="")`

January

```{r}
mydata<-d %>% filter(!is.na("C1Jan_days"))  %>% filter(C1Jan_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1Jan_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2018)),"  ", caption.percents, sep="")`

February

```{r}
mydata<-d %>% filter(!is.na("C1Feb_days"))  %>% filter(C1Feb_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1Feb_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2018)),"  ", caption.percents, sep="")`

March

```{r}
mydata<-d %>% filter(!is.na("C1Mar_days")) %>% filter(C1Mar_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1Mar_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2018)),"  ", caption.percents, sep="")`

April

```{r}
mydata<-d %>% filter(!is.na("C1Apr_days")) %>% filter(C1Apr_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1Apr_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2018)),"  ", caption.percents, sep="")`

May

```{r}
mydata<-d %>% filter(!is.na("C1May_days")) %>% filter(C1May_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1May_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2018)),"  ", caption.percents, sep="")`

June

```{r}
mydata<-d %>% filter(!is.na("C1June_days"))  %>% filter(C1June_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1June_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2018)),"  ", caption.percents, sep="")`

July

```{r}
mydata<-d %>% filter(!is.na("C1July_days"))  %>% filter(C1July_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1July_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2018)),"  ", caption.percents, sep="")`

August

```{r}
mydata<-d %>% filter(!is.na("C1Aug_days"))  %>% filter(C1Aug_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1Aug_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2018)),"  ", caption.percents, sep="")`

September

```{r SeptDays}
mydata<-d %>% filter(!is.na("C1Sept_days"))  %>% filter(C1Sept_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1Sept_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2018)),"  ", caption.percents, sep="")`

October

```{r}
mydata<-d %>% filter(!is.na("C1Oct_days"))  %>% filter(C1Oct_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1Oct_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2018)),"  ", "This table represents all respondants to this question including those who did not fish during the given time period.  ", caption.medians, "  ", labels.freq, sep="")`

```{r TotalDays}
mydata<-d %>% filter(!is.na("C1Total_days") & C1_AnsweredAll==TRUE) 
myFields<-mydata %>% select(contains("_days"))  %>% select(-contains("Total")) %>% names()
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  ArrangeTableMedians(base.summary.medians(mydata, myFields[i]) %>% mutate(Response=myFields[i]),
  roundDigits = 1)
}

CreateFt(LabelResponses(op,l))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2018)),"  ", "Only respondants that fished at least once during the time period were included in this breakdown.  ", caption.medians, "  ", labels.freq, sep="")`

```{r C1_medianDays}
mydata<-d %>% filter(!is.na("C1Total_days") & C1_AnsweredAll==TRUE)
myFields<-mydata %>% select(contains("_days")) %>% names()
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  ArrangeTableMedians(base.summary.medians(mydata %>% filter(get(myFields[i])>0), myFields[i]) %>% mutate(Response=myFields[i]),
  roundDigits = 1)
}

CreateFt(LabelResponses(op,l))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2018)),"  ", "Only respondants that fished at least once during the time period were included in this breakdown.  ", caption.medians, "  ", labels.freq, sep="")`

```{r C1_medianDaysJoyplot}
library(ggridges)
mydata %>%
  mutate(surveyYear=factor(surveyYear)) %>%
  filter(!is.na(C1Total_days)) %>%
  ggplot() +
  geom_density_ridges(aes(x=C1Total_days, y=surveyYear, fill=surveyYear),scale=5, rel_min_height=0.013 ) +
  scale_fill_viridis_d(begin=0.3, end=0.8) +
  labs(x="Total Days", y="") +
  theme_minimal() +
  theme(legend.position = "none")
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C2, 2018)), "  ", caption.means, "  ", labels.importance, sep="")`

```{r C2_motivations}
myFields<-d %>% dplyr::select(contains("C2")) %>% select(-contains("Answered")) %>% names()
op<-foreach(i=1:length(myFields), .combine = "rbind") %do% {
  base.summary.means(d, !!rlang::sym(myFields[i]))
}

CreateFt(ArrangeTable(SubstitueQuesForResponse(op, q, C2, 2018)))
```

```{r C2_likert, fig.width=7.5, fig.height=8}
op<-CreateSubScaleLikertGraphs(d, "Motivations", q)
```

<!---CHUNK_PAGEBREAK--->

```{r, fig.width=7.5, fig.height=8}
print(op[[1]])
```

<!---CHUNK_PAGEBREAK--->

```{r, fig.width=7.5, fig.height=8}
print(op[[2]])
```

<!---CHUNK_PAGEBREAK--->

```{r, fig.width=7.5, fig.height=8}
print(op[[3]])
```

<!---CHUNK_PAGEBREAK--->

```{r, fig.width=7.5, fig.height=8}
print(op[[4]])
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C2, 2018)), "  ", caption.means, "  ", labels.importance, sep="")`

```{r C2_table}
myFields<-c("motivation_pp","motivation_natural", "motivation_social","motivation_resource")
op<-foreach(i=myFields, .combine="rbind") %do% {
  base.summary.means(d%>% filter(get(paste(i,"_AnsweredAll", sep=""))==TRUE), !!rlang::sym(i))
}

CreateFt(ArrangeTable(LabelResponses(op, l)))
```

```{r C2_means}
CreateMeanPlot(LabelResponses(op, l), freeScale = FALSE, numCols=4) + theme(panel.background = element_rect(fill="gray80"))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C2, 2018)), "  ", caption.means, "  ", labels.importance, sep="")`

```{r}
myFields<-c("motivation_noncatch","motivation_catch")
op<-foreach(i=myFields, .combine="rbind") %do% {
  base.summary.means(d%>% filter(get(paste(i,"_AnsweredAll", sep=""))==TRUE), !!rlang::sym(i))
}

CreateFt(ArrangeTable(LabelResponses(op, l)))
```

`r paste(trimws(GetQuestion(q, C2, 2018)), "  ", caption.means, "  ", labels.importance, sep="")`

```{r C2_means_catch}
CreateMeanPlot(LabelResponses(op, l), freeScale = FALSE, numCols=4) + theme(panel.background = element_rect(fill="gray80"))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, E1, 2018)), "  ", caption.means, "  ", labels.agree, sep="")`

```{r E1, fig.height=8}
myFields<-d %>% dplyr::select(contains("E1")) %>% select(-contains("Answered")) %>% names()
op<-foreach(i=1:length(myFields), .combine = "rbind") %do% {
  base.summary.means(d, !!rlang::sym(myFields[i]))
}

CreateFt(ArrangeTable(SubstitueQuesForResponse(op, q, E1, 2018)))
```

<!---CHUNK_PAGEBREAK--->

```{r E1_likert, fig.width=7.5, fig.height=8}
op<-CreateSubScaleLikertGraphs(d, "Attitudes", q)
```

<!---CHUNK_PAGEBREAK--->

```{r, fig.width=7.5, fig.height=8}
print(op[[1]])
```

<!---CHUNK_PAGEBREAK--->

```{r, fig.width=7.5, fig.height=8}
print(op[[2]])
```

<!---CHUNK_PAGEBREAK--->

```{r, fig.width=7.5, fig.height=8}
print(op[[3]])
```

<!---CHUNK_PAGEBREAK--->

```{r, fig.width=7.5, fig.height=8}
print(op[[4]])
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, E1, 2018)), "  ", caption.means, "  ", labels.agree, sep="")`

```{r E1_means_subscales}
myFields<-c("attitude_catch", "attitude_numbers", "attitude_size", "attitude_harvest")

op<-foreach(i=myFields, .combine="rbind") %do% {
  base.summary.means(d%>% filter(get(paste(i,"_AnsweredAll", sep=""))==TRUE), !!rlang::sym(i))
}

CreateFt(ArrangeTable(LabelResponses(op, l)))
```

```{r E1_means_catch_noncatch}
CreateMeanPlot(LabelResponses(op, l), freeScale = FALSE, numCols=4) + theme(panel.background = element_rect(fill="gray80"))
toc()
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, F1, 2018)),"  ", caption.percents, sep="")`

```{r F1, fig.height=7}
myFields<-d %>% dplyr::select(contains("F1")) %>% select(-contains("Answered")) %>% select(-F1r) %>%names()

CreateFt(
  ArrangeTable(
    base.summary.percent.selectAll(d %>% filter(!(surveyYear==2012 & venue=="email") ), myFields, myAnsweredVar=F1_Answered),
    roundDigits=1)
  )

```


